Privacy-Respecting Type Error Telemetry at Scale

### 2023-12-05 programming23/paper.tex
sec 5 clarify 'contradiction'

      \item[- How often do projects contain modules with different modes?]
        Sessions rarely combine analysis modes.
        Only 512 of \nK{340} sessions ($<\pct{0.15}$) switched to modules with different
        analysis modes.
        This number may be a significant underapproximation because we have data
        only on modules that the creator chose to open, but the widespread use
        of \mnocheck{} mode suggests that it is not off by much.

>>>>

      \item[- How often do projects contain modules with different modes?]
        Sessions rarely combine analysis modes.
        Only 512 of \nK{340} sessions ($<\pct{0.15}$) switched to modules with different
        analysis modes.
        This number may be an underapproximation because we have data
        only on modules that the creator chose to open, but the widespread use
        of \mnocheck{} mode suggests that it is not off by much.
        If $\pct{90}$ of \emph{all} modules indeed use \mnocheck{}, then multi-mode
        projects must be rare.
